\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-15 paper/ms.tex
Finished sentence
Figure captions

\section{Running models}
To demonstrate \pkg{DNest4},
we will use a simple linear regression example where the
sampling distribution is
\begin{align}
y_i | m, b, \sigma &\sim \textnormal{Normal}(mx_i + b, \sigma^2)
\end{align}
and the priors are
\begin{align}
m &\sim \textnormal{Normal}(0, 1000^2)\\
b &\sim \textnormal{Normal}(0, 1000^2)\\
\ln\sigma &\sim \textnormal{Uniform}(-10, 10).
\end{align}
These are naive diffuse priors and we do not claim any special status for them.
This model was implemented in \proglang{C++}
(see Section~\ref{sec:models} for details) and is included in the
code/Examples/StraightLine subdirectory.

\begin{figure}[ht!]
\begin{minipage}{0.5\textwidth}
\includegraphics[width=8cm]{figures/fig1.pdf}
\caption{\label{fig:fig1}}
\end{minipage}
\begin{minipage}{0.5\textwidth}
\includegraphics[width=8cm]{figures/fig2.pdf}
\caption{\label{fig:fig2}}
\end{minipage}
\end{figure}

\begin{figure}[ht!]
\begin{minipage}{0.5\textwidth}
\includegraphics[width=8cm]{figures/fig3.pdf}
\caption{\label{fig:fig3}}
\end{minipage}
\begin{minipage}{0.5\textwidth}
\includegraphics[width=8cm]{figures/regression_lines.pdf}
\caption{Regression lines drawn from the posterior.
\label{fig:regression_lines}}
\end{minipage}
\end{figure}

@@

\code{-c <value>}\\
Standard DNS creates levels with a volume ratio of approximately
$e\approx 2.71828$. To use a different value, such as 10, use this option.
In our experience, \code{-c 10} tends to work better than the default
The output units remain in nats.
This option is incompatible with setting the maximum number of levels to 0
(automatic) in the OPTIONS file.
\\

>>>>

\section{Running models}
To demonstrate \pkg{DNest4},
we will use a simple linear regression example where the
sampling distribution is
\begin{align}
y_i | m, b, \sigma &\sim \textnormal{Normal}(mx_i + b, \sigma^2)
\end{align}
and the priors are
\begin{align}
m &\sim \textnormal{Normal}(0, 1000^2)\\
b &\sim \textnormal{Normal}(0, 1000^2)\\
\ln\sigma &\sim \textnormal{Uniform}(-10, 10).
\end{align}
These are naive diffuse priors and we do not claim any special status for them.
This model was implemented in \proglang{C++}
(see Section~\ref{sec:models} for details).
The dataset is shown in Figure~\ref{fig:regression_lines}
and the code is included in the
code/Examples/StraightLine subdirectory.

\begin{figure}[ht!]
\begin{minipage}{7.5cm}
\centering
\includegraphics[width=7cm]{figures/fig1.pdf}
\caption{The level $j$ of the saved particles over time.
Typically, this will trend upwards until all the levels have
been created, and then diffuse evenly throughout all the levels.
\label{fig:fig1}}
\end{minipage}\hspace{0.5cm}
\begin{minipage}{7.5cm}
\centering
\includegraphics[width=7cm]{figures/fig2.pdf}
\caption{{\bf Top panel}: The estimated compression factor between subsequent
levels, expressed as $\ln(X_{i+1}/X_{i})$. {\bf Bottom panel}:
The Metropolis acceptance fraction as a function of level.
\label{fig:fig2}}
\end{minipage}
\end{figure}

\begin{figure}[ht!]
\begin{minipage}{7.5cm}
\includegraphics[width=7cm]{figures/fig3.pdf}
\caption{{\bf Top panel}: The log-likelihood curve, showing the relationship
between log-likelihood and the enclosed prior mass.
{\bf Bottom panel}: Posterior weights of the saved particles.
For a successful run, there should be a clear peak, and saved particles
to the left of this plot should have insignificant posterior weight compared
to those in the peak.
\label{fig:fig3}}
\end{minipage}\hspace{0.5cm}
\begin{minipage}{7.5cm}
\includegraphics[width=7cm]{figures/regression_lines.pdf}
\caption{Regression lines drawn from the posterior.
\label{fig:regression_lines}}
\end{minipage}
\end{figure}

@@

\code{-c <value>}\\
Standard DNS creates levels with a volume ratio of approximately
$e\approx 2.71828$. To use a different value, such as 10, use this option.
In our experience, \code{-c 10} tends to work better than the default
value on problems with a large information.
The output units remain in nats.
This option is incompatible with setting the maximum number of levels to 0
(automatic) in the OPTIONS file.
\\
